TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-09-21 paper/draft.tex
wording

\apogee\ is primarily targeted for bright stellar populations, with de-reddened photometry and color cutoffs of $7 \leq H \leq 13.8$ and $[J-K]_0 \geq 0.5$ \citep{Zasowski:2013} with the objective of studying galactic composition and evolution. However numerous cool, main sequence sources have also been observed either as targets proposed by the M dwarf ancilliary survey (1,350 sources selected by proper motions from the  \citealt{Desphande:2013}), or randomly by \apogee\, which we quantify in this study to be over 10,000 in total.

>>>>

\apogee\ is primarily targeted for bright stellar populations, with de-reddened photometry and color cutoffs of $7 \leq H \leq 13.8$ and $[J-K]_0 \geq 0.5$ \citep{Zasowski:2013} with the objective of studying galactic composition and evolution. However numerous cool, main sequence sources have also been observed either as targets proposed by the M dwarf ancilliary survey (1,350 sources selected by proper motions; \citealt{Desphande:2013}), or randomly by \apogee\, which we quantify in this study to be over 10,000 in total.
